Full Dissertation

### 2024-04-04 Sections/full.qmd
redo

---
title: Full Dissertation
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
date: last-modified
#page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: true
    output-file: diss_full_gfm.md
editor: 
  markdown: 
    wrap: 72
prefer-html: true
---

>>>>

---
title: Full Dissertation
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
date: 04/04/24
#page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: true
    output-file: diss_full_gfm.md
editor: 
  markdown: 
    wrap: 72
prefer-html: true
---
